State of the Practice for Lattice Boltzmann Method Software

### 2022-02-17 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Minor edits to SOP for LBM paper

To focus our efforts, we devised 11 research questions.  The questions are used
to structure the discussion in the paper, so for each research question below we
point to the section that contains our answer.  The questions are inspired by
the research questions that underpin our data collection methodology
\citep{SmithEtAl2021}. We start with identifying the examples of LBM software
where we have access to the source code:

@@

>>>>

To focus our efforts, we devised 10 research questions.  The questions are used
to structure the discussion in the paper, so for each research question below we
point to the section that contains our answer.  The questions are inspired by
the research questions that underpin our data collection methodology
\citep{SmithEtAl2021}. We start with identifying the examples of LBM software
where we have access to the source code:

@@

\wss{From Peter: The developer of ESPResSo mentioned ``tests which compare
implementations against each other, like say if there's to solve us for
electrostatic switch rely on different principles and they've been written by
different people''.
The developer of TCLB also mentioned automatic testing. They discussed the idea
of using test cases, but concerns were raised with this, such as the required
computing power to run such tests frequently and where to store large amounts of
data. Also, ``constructing such cases would be very hard''.
The developer of OpenLB commented that they have different kinds of tests, such
as integration tests, and tests where they know the ``exact analytical solution''.
They also mentioned comparing computations and ``check[ing] the misfits''.}
